Regular singular Volterra equations on complex domains

### 2023-07-30 reg-sing-volterra.tex
Finish drafting introduction
Include older draft paragraphs in comments. Also, correct name alphabetization.

%%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{rmk}{Remark}

@@

\title{Regular singular Volterra equations on complex domains}
\author{Aaron Fenyes and Veronica Fantini}
\date{}

@@

\item Finish introduction

@@

\item \textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.

@@

        \item \textit{(Veronica)} Add motivation to Section~\ref{sec:image under soft_part}, explaining that the desired result of the section follows from a more general result about the smoothing effect of $\softpart$ (Proposition~\ref{prop:smoothing}).

@@

    \item Decide whether to keep Lemma~\ref{thm:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary. Change order as appropriate.

@@

    \item Choose subscripts or decorations to tell things apart in equations.

@@

z^{-\lambda} \laplace \varphi & = \laplace\,\fracderiv{-\lambda}{}{} \varphi,

@@

where $\fracderiv{-\lambda}{}{}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on differential equations.

If you pull back a nice enough differential operator, you might get a Volterra operator with a real-analytic kernel. This extends uniquely to a holomorphic Volterra operator on a complex extension of the position domain. \textcolor{orange}{[...]}

\textcolor{RoyalBlue}{If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically.}
\begin{brainstorm}
    \item \textit{Brainstorm motivation ideas here\ldots}
\end{brainstorm}
\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. We also assume:
\begin{itemize}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
\end{itemize}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

@@

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
\begin{itemize}
\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
\end{itemize}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\begin{itemize}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
\[ \big| \hardker(a, a') \big| \textcolor{magenta}{\lesssim} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
%%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
\end{itemize}
\subsubsection{The perturbed operator}\label{setting:perturbed}
We'll generalize $\hardpart$ by adding a perturbation $\softpart$ that doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}). To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{itemize}
\condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}\label{thm:basic_volterra}
Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
\[ f = \hardpart f \]
have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

@@

We'll prove this result in Sections~\ref{sec:existence and uniqueness}: by Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{thm:perturbed_volterra}.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\lambda_0}$.
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in.
    \item Use the contraction mapping theorem to prove Lemma~\ref{thm:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}

@@

\begin{align*}
|f_0| & \leq C_1 |\zeta(a)|^\tau \, \exp\big(\tfrac{3}{2}\varepsilon\delta\big) \left\vert  \frac{p(b)}{p(a)}\right\vert \\
& = C_2 |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
& \leq C_3 |\zeta(a)|^{\tau-1}.
\end{align*}
The last step uses Condition~\eqref{cond:sing}. 
\end{proof}

@@

In particular, 
      \begin{align*}
          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
          &\leq C  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
          & \leq C |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
      \end{align*}
   which is bounded because $|\zeta(a)|>\delta$.

@@

>>>>

%%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{rmk}{Remark}
\newtheorem{cor}{Corollary}

@@

\title{Regular singular Volterra equations on complex domains}
\author{Veronica Fantini and Aaron Fenyes}
\date{}

@@

\item \textit{(Aaron)} Finish introduction

@@

\item \textcolor{gray}{\textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.}

@@

        \item \textit{(Veronica)} Add motivation to Section~\ref{sec:image under soft_part}, explaining that the desired result of the section follows from a more general result about the smoothing effect of $\softpart$ (Proposition~\ref{prop:smoothing}). \textcolor{green}{I added a Corollary to explicitly write how Proposition \ref{prop:smoothing} implies the regularity we want for $\softpart f_0$}

@@

    \item \textcolor{gray}{Decide whether to keep Lemma~\ref{thm:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary. Change order as appropriate.} \textcolor{purple}{Keep Lemma~\ref{thm:perturbed_volterra} as a lemma. State it after Theorem~\ref{thm:general_volterra}.}

@@

    \item \textcolor{gray}{Choose subscripts or decorations to tell things apart in equations.} Change $\hardpart$ with $\volterra_0$ and $\softpart$ with $\volterra_\star$. Same for $\hardker$ and $\softker$. 

@@

z^{-\lambda} \laplace \varphi & = \laplace\,\partial^{-\lambda} \varphi,

@@

where $\partial^{-\lambda}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on differential equations.

Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain. Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \textcolor{orange}{\cite{EcalleIII}\cite{lectures-marino}}.

\textcolor{RoyalBlue}{A nice feature of the Laplace transform is that} Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain. In Section~\ref{sec:example}, we'll see this \textcolor{purple}{helpful} behavior in the class of differential equations that Ecalle calls {\em level $1$}, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate. This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}. \textcolor{RoyalBlue}{In Section~\ref{sec:example}, we'll see this behavior in the class of differential equations that Ecalle calls {\em level $1$}, which includes classical and not-so-classical examples like the modified Bessel equation; some cases of the equation describing the vibration modes of a beam \textcolor{orange}{[find citation]}, and---after a change of coordinate---the Airy, Airy-Lucas~\cite[Equation 3.2]{charbonnier22}, higher Airy~\cite[Equation 3.8]{charbonnier22}\cite{durugo_higher}, and generalized Airy equations \cite[Equation 9.13.31]{dlmf}.}

From our experience with solving level 1 differential equations by Borel summation, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity. Let's say we've chosen the position variable $\zeta$ so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity. Assuming the residue $\tau$ is real and positive, we expect to find a solution with the following features:
\begin{itemize}
\item It has an $O\big(\zeta^{\tau-1}\big)$ singularity at $\zeta = 0$.
\item It's of exponential type, meaning that it's $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
\end{itemize}
These conditions are just strong enough to ensure that the solution has a well-defined Laplace transform, which by construction will satisfy the differential equation we started with in the frequency domain. The first condition also tells us that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
%%\begin{itemize}
%%\item They have singularities that look like $(\zeta - \alpha)^{\tau-1}$ with $\tau > 0$, where $\zeta$ is the position variable and $\zeta = \alpha$ is a place where the Volterra equation has a regular singularity.
%%\item They're of exponential type.
%%\item They grow slowly enough as $|\zeta| \to \infty$ to have well-defined Laplace transforms, which by construction will satisfy the differential equation we started with in the frequency domain.
%%\end{itemize}
%%Thanks to their mild singularities and moderate growth, these solutions have well-defined Laplace transforms, which by construction will satisfy the differential equation we started with in the frequency domain.
%%This has led us to look for solutions of regular singular Volterra equations in the the function spaces defined in Section~\ref{fn-spaces}, which are designed to capture the properties above. \textcolor{orange}{[Describe existence and uniqueness result.]}

Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}. We'll achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}. \textcolor{orange}{[Mention treatment of motivating example in Section~\ref{sec:example}.]}

% -------------------------------------------

%%If you pull back a nice enough differential operator, you might get a Volterra operator with a real-analytic kernel, which extends uniquely to a holomorphic Volterra operator on a complex extension of the position domain. By analytically continuing the eigenfunctions of the Volterra operator around singularities in the position domain, you might discover hidden relationships between the eigenfunctions of the original differential operator. In its nicest cases, this phenomenon is called {\em resurgence} \textcolor{orange}{[cite]}.

\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. We also assume:
\begin{itemize}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
\end{itemize}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

@@

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
\begin{itemize}
\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
\end{itemize}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\begin{itemize}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
\[ \big| \hardker(a, a') \big| \leq \,  \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
%%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
\end{itemize}
\subsubsection{The perturbed operator}\label{setting:perturbed}

Now, let's perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$. The perturbation $\softpart$ doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}). To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{itemize}
\condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| k_\text{extra} (a, a') \big| \leq \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

Like $\hardker$, the combined kernel $k = \hardker + \softker$ of $\volterra$ grows in a controlled way when its arguments are near $\zeta = 0$, and when the difference between its arguments grows. We'll provide specific bounds in Section~\ref{sec:bounds on k}.

\subsection{Main results}\label{sec:results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\begin{thm}\label{thm:basic_volterra}
Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
\[ f = \hardpart f \]
have the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

@@

We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{thm:perturbed_volterra}.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{thm:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
 When $\hardpart$ satisfies Condition \eqref{cond:sing} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$. Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$

\[ \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert \leq \varepsilon\]

Then,

\begin{align*}
    |k(a,a')&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
    &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
\end{align*}

\textcolor{orange}{[edit to emphasize instead that we can make $\sigma - \tau$ arbitrarily small]} 
The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small. We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

Similarly, we can estimate the kernel $k$ far from $\zeta=0$. Assuming $\hardpart$ satisfies Condition \eqref{cond:diag-basic} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, for $|\zeta(a)|\geq \delta$ and for every $a'\in\Omega$

\begin{align*}
    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
\end{align*}
Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like

\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]

We deduce that

\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]

with $M= \textcolor{magenta}{C_\Delta} + \delta \textcolor{magenta}{C_k}$.

\color{purple}If $\epsilon\in (0,1]$, we actually get a better estimate, namely

\[ |k(a,a')| \leq M\textcolor{magenta}{(a')}\, e^{ \lambda_\Delta |\zeta(a)-\zeta(a')|} \]

with $M\textcolor{magenta}{(a')} = \textcolor{magenta}{C_\Delta} + (\delta^{\epsilon-1}+\delta |\zeta(a')|^\epsilon ) \,  \textcolor{magenta}{C_k}$.\color{black}

\begin{verify}
    \begin{align*}
        \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
        &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
        &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
    \end{align*}
\end{verify}

%notice that $\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon$ is bounded by a constant which depends on $|\zeta(a')|$ (and of course on $\delta$ and $\epsilon$)

\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}

@@

\begin{align*}
|f_0| &  \leq C_1 |\zeta(a)|^\tau \, \exp\big(\tfrac{3}{2}\varepsilon\delta\big) \left\vert  \frac{p(b)}{p(a)}\right\vert \\
& =  C_2 |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
&  \leq C_3 |\zeta(a)|^{\tau-1}.
\end{align*}

The last step uses Condition~\eqref{cond:sing}. 
\end{proof}

@@

In particular, 
      \begin{align*}
          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
          & \textcolor{magenta}{\lesssim}  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
          & \textcolor{magenta}{\lesssim}  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
      \end{align*}
   which is bounded because $|\zeta(a)|>\delta$.

@@

In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$. This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
